---
title: "RWorksheet_Layson#3b"
author: "Gilmar Layson"
date: "2024-10-07"
output: pdf_document
---


#1. a.
```{r}
datafr <- data.frame(
  Respondents = c(1:20), 
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2),
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
  Persons_at_home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 8, 4, 7, 8, 8, 3, 11, 7, 6),
  Siblings_at_school = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
  Types_of_houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2)
)
datafr
```
#b.
```{r}
str(datafr)
summary(datafr)
```

#c.
```{r}
mean(datafr[,5])
```

#d.
```{r}
first2 <- datafr[1:2, ]
first2

#e.
```


row_and_col <- datafr[c(3,5), c(2,4)]
row_and_col

#f.

```{r}

types_houses <- datafr[ ,6]
types_houses
```

#g.

```{r}
Farm_Male <- subset(datafr, datafr[,2] == 1 & datafr[,3] == 1 )
Farm_Male
```

#h.
```{r}
Female_Res <- subset(datafr, datafr[,2] == 2 & datafr[,5] >= 5)
Female_Res

```
#2.
```{r}
df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
```


#a.
#Five columns (Int, Doubles, Characters, Logicals, and Factors) with different data types (integer, numeric, character, logical, and factor) but no observations and make up the empty data frame.

#3
a.
```{r}
household <- read.csv("HouseholdData.csv", header = TRUE)
household
```


b.
```{r}
factor(household[,2], levels = c("Male", "Female"), labels = c(1,2))
```
c.

```{r}
factor(household[,6], levels = c("Wood", "Congrete", "Semi-congrete"), labels = c(1,2,3))
```
d.
```{r}
factor(household[,3], levels = c(1,2,3), labels = c("Farmer", "Driver", "Others"))
```
e.
```{r}
subset(household[,c(2,3)], household[,2] == 2 & household[,3] == "Driver")
```

f.
```{r}
subset(household, household[,5] >= 5)
```

#4.
#The data table describes the demographics of 10 respondents, including their sex, the jobs held by their fathers, the number of people living at home, the number of siblings enrolled in school, and the kinds of homes they reside in.